\textbf{{\Large {Recursive algorithms, branching coefficients and applications}}}

### 2010-06-21 AffineLieAlgebras/InformalNotes/article.tex
Some misprints fixed

In the case of special embeddings the set $\Delta^{+}_{\bot}$ can be empty as for the
special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $A_1\subset A_2\subset A_3$ which is depicted at the Figure \ref{fig:a1a2a3}. 
\begin{figure}[h]
\noindent  \centering{
  \includegraphics[width=80mm]{special_A1_A2_A3.pdf}
  \caption{Special embedding $A_1\subset A_2\subset A_3$. Grey vectors are the roots of $A_2$, thick black - of $\mathfrak{a}=A_1$, dashed black are the orthogonal roots of $A_1$ which is contained in $\mathfrak{a}_{\bot}$ }
}
  \label{fig:a1a2a3}
\end{figure}

@@

Consider the regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are drawn as the dashed vectors at the Figure \ref{fig:B2_A1}. We denote the corresponding Weyl reflections by $\omega_1, \omega_2$. Simple root $\beta$ of the embedded $A_1$ is equal to $\alpha_1+2\alpha_2$ and is drawn as the grey vector.

@@

Firstly we construct the fan for this injection.
Using the definition (\ref{fan-defined}) we obtain the set $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$, depicted at the Figure \ref{fig:B4B2Fan}.

@@

We see that inside $\bar{C}_{\hat{A}_1}$, which is shown at the Figure \ref{fig:AffineA2_A1_branching}, there are only two non-zero anomalous weights. These are the branching coefficients. So the finite reducibility theorem holds and we get the decomposition
\begin{equation}
  \label{eq:43}
  L^{(0,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(0;4;0)}\oplus L_{\hat{A_1}}^{(4;4;0)}.
\end{equation}

@@

Consider the embedding $\mathfrak{a}\subset \mathfrak{g}$ where $\mathfrak{a}=\hat A_1\oplus \hat A_1$ and $\mathfrak{g}= \hat A_3$, which is the affine extension of the special embedding $A_1\oplus A_1\subset A_3$. Let's construct the special embedding $A_1\oplus A_1\subset A_3$ using the method of \cite{vasilevich1986method}. We start with 4-dimensional representation of $A_1\oplus A_1$ with the highest weight $(1,1)$. The weights of this representation are numbered as depicted at the Figure \ref{fig:A_1+A_1_to_A3} and have the following coordinates in the fundamental weights basis: $\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)$.

@@

Then for the matrix elements of representation of Cartan subalgebra generators $b_1,b_2$ in Weyl basis we have $d(b_i)=\mathrm{diag}\left(\frac{2(\nu_1,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_2,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_3,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_4,\alpha_i)}{(\alpha_i,\alpha_i)}\right)$ \cite{vasilevich1986method}, so $d(b_1)=\mathrm{diag}(1,-1,1,-1),\; d(b_2)=\mathrm{diag}(1,1,-1,-1)$.  The embedded roots $\alpha_1,\alpha_2$ of $A_1\oplus A_1$ in terms of roots $\tilde{\alpha}_i$ of $A_3$ are
\begin{equation}
  \label{eq:37}
  \begin{array}{l}
     \alpha_1=\frac{1}{2}(\tilde{\alpha}_1+\tilde{\alpha}_3)\\
     \alpha_2=\frac{1}{2}(\tilde{\alpha}_1+2\tilde{\alpha}_2+\tilde{\alpha}_3)
  \end{array}
\end{equation}
They are depicted at the Figure \ref{fig:A1+A1-A3}.

@@

The set $\Delta^{+}_{\bot}$ is empty. 
The fan $\Gamma _{\frak{a}\subset \frak{g}}$ is shown at the Figure \ref{fig:A1+A1-A3_fan}. Coordinates of fan element's finite part are given in the basis of fundamental roots of $A_1\oplus A_1$. Element $\gamma$ is shown by cross if  $s(\gamma)=1$ and by diamond if $s(\gamma)=-1$.
\begin{figure}[h!tb]
  \includegraphics[width=135mm]{A1+A1-A3_fan.pdf}
  \caption{Fan for the special embedding $\hat A_1\oplus\hat A_1\subset\hat A_3$}
  \label{fig:A1+A1-A3_fan}
\end{figure}

@@

The set  $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of $L^{w_2}_{\hat A_3}$ consists of 192 elements and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for $\mu=w_2=(0,1,0;1;0)$ is shown at the Figure \ref{fig:A1+A1-A3_anom}. Coordinates of anomalous weight's finite part are given in the basis of fundamental weights of $A_1\oplus A_1$. The weights are shown by crosses if the determinant has the value $\epsilon(\omega)=1$ and by diamonds otherwise.

@@

The anomalous branching coefficients for the module $L^{(w_2)}$ are shown at the Figure  \ref{fig:A1+A1-A3_branching}. The anomalous branching coefficients in the $C_{\frak{a}}$ are equal to the branching coefficients of $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$ and are shown by the stars in the Figure \ref{fig:A1+A1-A3_branching}.
%\begin{figure}[h!tb]
\begin{figure}[p]
%  \hspace*{-1cm}
  \includegraphics[width=135mm,height=85mm]{A1+A1-A3_branching.pdf}
  \caption{Anomalous branching coefficients for $L^{w_2}_{\hat A_3}$}
  \label{fig:A1+A1-A3_branching}
\end{figure}

@@

\begin{figure}[h!tb]
%  \hspace*{-2cm}
  \includegraphics[width=140mm]{AffineB2_A1_Anom.pdf}
  \caption{The anomalous weights of the $L^{(1,0;1;0)}_{\hat B_2 }$. The weights of the grade 0 are depicted at the Figure \ref{fig:B2_A1}}.
  \label{fig:affine_B2_anom_point}
\end{figure}

>>>>

In the case of special embeddings the set $\Delta^{+}_{\bot}$ can be empty as for the
special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $A_1\subset A_2\subset A_3$ which is depicted in the Figure \ref{fig:a1a2a3}. 
\begin{figure}[h]
\noindent  \centering{
  \includegraphics[width=80mm]{special_A1_A2_A3.pdf}
  \caption{Special embedding $A_1\subset A_2\subset A_3$. Grey vectors are the roots of $A_2$, thick black - of $\mathfrak{a}=A_1$, dashed black are the orthogonal roots of $A_1$ which is contained in $\mathfrak{a}_{\bot}$ }
}
  \label{fig:a1a2a3}
\end{figure}

@@

Consider the regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are drawn as the dashed vectors in the Figure \ref{fig:B2_A1}. We denote the corresponding Weyl reflections by $\omega_1, \omega_2$. Simple root $\beta$ of the embedded $A_1$ is equal to $\alpha_1+2\alpha_2$ and is drawn as the grey vector.

@@

Firstly we construct the fan for this injection.
Using the definition (\ref{fan-defined}) we obtain the set $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$, depicted in the Figure \ref{fig:B4B2Fan}.

@@

We see that inside $\bar{C}_{\hat{A}_1}$, which is shown in the Figure \ref{fig:AffineA2_A1_branching}, there are only two non-zero anomalous weights. These are the branching coefficients. So the finite reducibility theorem holds and we get the decomposition
\begin{equation}
  \label{eq:43}
  L^{(0,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(0;4;0)}\oplus L_{\hat{A_1}}^{(4;4;0)}.
\end{equation}

@@

Consider the embedding $\mathfrak{a}\subset \mathfrak{g}$ where $\mathfrak{a}=\hat A_1\oplus \hat A_1$ and $\mathfrak{g}= \hat A_3$, which is the affine extension of the special embedding $A_1\oplus A_1\subset A_3$. Let's construct the special embedding $A_1\oplus A_1\subset A_3$ using the method of \cite{vasilevich1986method}. We start with 4-dimensional representation of $A_1\oplus A_1$ with the highest weight $(1,1)$. The weights of this representation are numbered as depicted in the Figure \ref{fig:A_1+A_1_to_A3} and have the following coordinates in the fundamental weights basis: $\nu_1=(1,1),\; \nu_2=(-1,1),\; \nu_3=(1,-1),\; \nu_4=(-1,-1)$.

@@

Then for the matrix elements of representation of Cartan subalgebra generators $b_1,b_2$ in Weyl basis we have $d(b_i)=\mathrm{diag}\left(\frac{2(\nu_1,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_2,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_3,\alpha_i)}{(\alpha_i,\alpha_i)},\frac{2(\nu_4,\alpha_i)}{(\alpha_i,\alpha_i)}\right)$ \cite{vasilevich1986method}, so $d(b_1)=\mathrm{diag}(1,-1,1,-1),\; d(b_2)=\mathrm{diag}(1,1,-1,-1)$.  The embedded roots $\alpha_1,\alpha_2$ of $A_1\oplus A_1$ in terms of roots $\tilde{\alpha}_i$ of $A_3$ are
\begin{equation}
  \label{eq:37}
  \begin{array}{l}
     \alpha_1=\frac{1}{2}(\tilde{\alpha}_1+\tilde{\alpha}_3)\\
     \alpha_2=\frac{1}{2}(\tilde{\alpha}_1+2\tilde{\alpha}_2+\tilde{\alpha}_3)
  \end{array}
\end{equation}
They are depicted in the Figure \ref{fig:A1+A1-A3}.

@@

The set $\Delta^{+}_{\bot}$ is empty. 
The fan $\Gamma _{\frak{a}\subset \frak{g}}$ is shown in the Figure \ref{fig:A1+A1-A3_fan}. Coordinates of fan element's finite part are given in the basis of fundamental roots of $A_1\oplus A_1$. Element $\gamma$ is shown by cross if  $s(\gamma)=1$ and by diamond if $s(\gamma)=-1$.
\begin{figure}[h!tb]
  \includegraphics[width=135mm]{A1+A1-A3_fan.pdf}
  \caption{Fan for the special embedding $\hat A_1\oplus\hat A_1\subset\hat A_3$}
  \label{fig:A1+A1-A3_fan}
\end{figure}

@@

The set  $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of $L^{w_2}_{\hat A_3}$ consists of 192 elements and its projection $\pi_{\mathfrak{a}}\left(\widehat{\Psi^{(\mu)}}\right)$ for $\mu=w_2=(0,1,0;1;0)$ is shown in the Figure \ref{fig:A1+A1-A3_anom}. Coordinates of anomalous weight's finite part are given in the basis of fundamental weights of $A_1\oplus A_1$. The weights are shown by crosses if the determinant has the value $\epsilon(\omega)=1$ and by diamonds otherwise.

@@

The anomalous branching coefficients for the module $L^{(w_2)}$ are shown in the Figure  \ref{fig:A1+A1-A3_branching}. The anomalous branching coefficients in the $C_{\frak{a}}$ are equal to the branching coefficients of $L^{w_2}_{\hat A_3\downarrow \hat{A_1}\oplus\hat{A_1}}$ and are shown by the stars in the Figure \ref{fig:A1+A1-A3_branching}.
%\begin{figure}[h!tb]
\begin{figure}[p]
%  \hspace*{-1cm}
  \includegraphics[width=135mm,height=85mm]{A1+A1-A3_branching.pdf}
  \caption{Anomalous branching coefficients for $L^{w_2}_{\hat A_3}$}
  \label{fig:A1+A1-A3_branching}
\end{figure}

@@

\begin{figure}[h!tb]
%  \hspace*{-2cm}
  \includegraphics[width=140mm]{AffineB2_A1_Anom.pdf}
  \caption{The anomalous weights of the $L^{(1,0;1;0)}_{\hat B_2 }$. The weights of the grade 0 are depicted in the Figure \ref{fig:B2_A1}}.
  \label{fig:affine_B2_anom_point}
\end{figure}
